One more attempt on ArXe

### 2016-05-16 theo_results.tex
small reformulations

Because the structures have only one xenon atom, ETMD(3) is not possible
and only ICD is expected. 
%Both spectra show several smaller peaks which
%are convoluted into one single peak with a maximum at
%approximately \unit[0.2]{eV}. 
%In comparison to the 13 argon atoms core
%spectrum t
The spectrum pertaining to the clusters with larger (55 atom) Ar core shows
signals at higher energies of the secondary electron. These features
can be explained by looking at the Ar-Xe distances in the clusters, shown
in the bottom panel of Figure \ref{figure:surf}. 
Every different atom pair distance
yields in a different energy of the secondary electron and only pairs
with a distance of larger than the channel opening distance
(dashed, gray line) will contribute
to the spectrum. 
%In our model, there is a one-to-one correspondence between interatomic distance $d$ and kinetic energy of the ICD electron.
The larger the interatomic distance, the higher is the
kinetic energy of the secondary electron for a given channel.
Since the 55 argon atom core cluster is larger and therefore
has Ar-Xe pairs with larger distances its spectrum is extended to
higher energies.
%energies as well.
This effect holds for all clusters.
%This explains why the ICD spectrum for larger clusters extends to higher energies, and holds for all cluster structures.

>>>>

Because the structures have only one xenon atom, ETMD(3) is not possible
and only ICD is expected. 
%Both spectra show several smaller peaks which
%are convoluted into one single peak with a maximum at
%approximately \unit[0.2]{eV}. 
%In comparison to the 13 argon atoms core
%spectrum t
The spectrum pertaining to the clusters with larger (55 atom) Ar core shows
signals at higher energies of the secondary electron. These features
can be explained by looking at the Ar-Xe distances in the clusters, shown
in the bottom panel of Figure \ref{figure:surf}. 
Every different atom pair distance
yields in a different energy of the secondary electron and only pairs
with a distance of larger than the channel opening distance
(dashed, gray line) will contribute
to the spectrum. 
%In our model, there is a one-to-one correspondence between interatomic distance $d$ and kinetic energy of the ICD electron.
The larger the interatomic distance, the higher is the
kinetic energy of the secondary electron for a given channel.
Since the cluster with an Ar core of 55 atoms is larger, and therefore
contains Ar-Xe pairs with larger distances, its spectrum extends to
higher energies.
%energies as well.
This relation between ICD energy and cluster size holds true for all cluster structures.
%This explains why the ICD spectrum for larger clusters extends to higher energies, and holds for all cluster structures.
